Fixing Vulnerabilities Hinders Maintainability

### 2019-02-10 paper/ICPC19/icpc19.tex
major updates
fix..?
icpc19 2nd submission version

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage[table,xcdraw]{xcolor}
\usepackage{framed}
\usepackage{float}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{xfrac}

@@

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.8\linewidth]{figures/commit.pdf}
 	\caption{Maintainability difference for security commits}
	\label{fig:commit}
\end{figure}

@@

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.5\textwidth]{figures/maintainability.pdf}
 	\caption{Maintainability difference for security and baseline refactorings}
	\label{fig:secvsreg}
\end{figure}

@@

We have also evaluated the impact on the maintainability per programming language
of open-source software, Figure~\ref{fig:lang_main}. Although
the dataset contains security refactorings for more than $13$ languages, we only
present the results for \emph{Java}, \emph{C}, \emph{Ruby}, and \emph{PHP}
because the Paired Wilcoxon signed-rank requirement: input sample has to have more 
than $20$ samples. The other languages were
integrated into \emph{Others}. The results of the Paired Wilcoxon signed-rank
test by pattern indicate that there is statistical evidence to support that the
maintainability of open-source software decreases for security refactorings in
$3$ different languages: \emph{C} (p-value = $5.72$x$10^{-9}$), Ruby (p-value = $0.057$) and
PHP (p-value = $3.54$x$10^{-6}$). The results also provide statistical significance
for when security refactorings are performed in \emph{Java} (p-value =
$3.61$x$10^{-2}$). \emph{Python} and the languages that integrate the
\emph{Others} set contain more cases where the maintainability increases.
However, the results obtained for these patterns are not statistically
significant.

>>>>

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage[table,xcdraw]{xcolor}
\usepackage{framed}
\usepackage{float}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{xfrac}

@@

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.75\linewidth]{figures/commit.pdf}
 	\caption{Maintainability difference for security commits}
	\label{fig:commit}
\end{figure}

@@

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.46\textwidth]{figures/maintainability.pdf}
 	\caption{Maintainability difference for security and baseline refactorings}
	\label{fig:secvsreg}
\end{figure}

@@

We have also evaluated the impact on the maintainability per programming language
of open-source software, Figure~\ref{fig:lang_main}. Although
the dataset contains security refactorings for more than $13$ languages, we only
present the results for \emph{Java}, \emph{Python}, \emph{C}, \emph{Ruby}, and \emph{PHP}
because of the Paired Wilcoxon signed-rank test requirement: input sample has to have more 
than $20$ samples. The other languages were
integrated into \emph{Others}. The results of the Paired Wilcoxon signed-rank
test by pattern indicate that there is statistical evidence to support that the
maintainability of open-source software decreases for security refactorings in
$3$ different languages: \emph{C} (p-value = $5.72$x$10^{-9}$), Ruby (p-value = $0.057$) and
PHP (p-value = $3.54$x$10^{-6}$). Following the \textit{American Statistical Association} recommendations~\cite{doi:10.1080/00031305.2016.1154108}, 
we consider the results for Ruby as statistically significant because its p-value is on the borderline.
The results also exhibit statistical significance
for when security refactorings are performed in \emph{Java} (p-value =
$3.61$x$10^{-2}$). \emph{Python} and the languages that integrate the
\emph{Others} set contain more cases where the maintainability increases.
However, the results obtained for these patterns are not statistically
significant.
